Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population

### 2023-11-03 analysis/paper/paper.qmd
feat: formatting for PCI_Archaeo
bump version to 0.1.0

@@

All raw data is available on Zenodo (<https://doi.org/10.5281/zenodo.8061483>).
Analysis scripts, and the source code for the manuscript and
supplementary materials are available as a research compendium
(<https://doi.org/10.5281/zenodo.7649825>)
using the structure recommended by the **rrtools** R package [@Rrrtools].

@@

>>>>

## Funding {-}

@@

@@

All raw data is available on Zenodo (<https://doi.org/10.5281/zenodo.8061483>).
Analysis scripts, and the source code for the manuscript and
supplementary materials are available as a research compendium
(<https://doi.org/10.5281/zenodo.7649824>)
using the structure recommended by the **rrtools** R package [@Rrrtools].
